Time slice analyses

### 2017-11-23 analyses/02-time-slice-analyses.Rmd
cleaned up former analysis drafts

## The latest version of dispRity on master branch
## install_github("TGuillerme/dispRity", ref = "master")
library(dispRity)

@@

```{r, eval = FALSE, echo = FALSE}
## Testing data: TO REMOVE
#TG: it's just faster this way
#TG: also, I've only tested it on "Epoch" since it take ages to run, should be pipelined all right though
data(BeckLee_mat99)
data(BeckLee_tree)
data(BeckLee_ages)

morphospace <- BeckLee_mat99
tree <- BeckLee_tree
FADLAD <- BeckLee_ages

@@

<!-- TG: I've not run this analysis below -->
<!-- We also ran the models using varying numbers of bins as follows. -->

```{r, eval = FALSE, echo = FALSE}
## Run the function for Beck data
slug <- "BeckLee"

for (bins in c(2, 5, 10, 15, 20)){
  output <- run.all.disparity(morphospace, tree, bins, FADLAD, inc.nodes = TRUE,
                              bootstraps = 100, metric = c(sum, variances), metric.name = "sum_var")

  readr::write_csv(output, path = paste0("../outputs/bins", "_", slug, ".csv"), append = TRUE)
}

<!-- NC: Need to think more about the outputs here, currently they don't make much sense as there are no column headers -->

@@

>>>>

## The latest version of dispRity on release branch #TG: master is under many changes!
## install_github("TGuillerme/dispRity", ref = "release")
library(dispRity)

@@

@@

@@

## Comparing the disparity through time curves

```{r}
curve1 <- out2$object[[1]][[1]]
curve2 <- out2$object[[1]][[2]]
curve3 <- out2$object[[1]][[3]]
curve4 <- out2$object[[1]][[4]]
curve5 <- out2$object[[1]][[5]]
